Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Proof-of-Concept V}}

### 2014-08-03 Paper.tex
Typo.

As previously detailed, $\mathbf{R}[n]_{\boldsymbol{\sigma}}$ and $\mathbf{R}[n]_u$ are the $n$th corresponding states and cumulative gas used after each transaction. The former is defined simply as the state resulting from applying the corrresponding transaction to the state resulting from the previous transaction (or the block's initial state in the case of the first such transaction):
\begin{equation}
B_\mathbf{R}[n]_{\boldsymbol{\sigma}} = \begin{cases} \Gamma(B) & \text{if} \quad n < 0 \\ \Upsilon(B_\mathbf{R}[n - 1]_{\boldsymbol{\sigma}}, B_\mathbf{T}[n]) & \text{otherwise} \end{cases}
\end{equation}

>>>>

As previously detailed, $\mathbf{R}[n]_{\boldsymbol{\sigma}}$ and $\mathbf{R}[n]_u$ are the $n$th corresponding states and cumulative gas used after each transaction. The former is defined simply as the state resulting from applying the corresponding transaction to the state resulting from the previous transaction (or the block's initial state in the case of the first such transaction):
\begin{equation}
B_\mathbf{R}[n]_{\boldsymbol{\sigma}} = \begin{cases} \Gamma(B) & \text{if} \quad n < 0 \\ \Upsilon(B_\mathbf{R}[n - 1]_{\boldsymbol{\sigma}}, B_\mathbf{T}[n]) & \text{otherwise} \end{cases}
\end{equation}
